Differentially Private Bayesian Inference

### 2018-02-16 main.tex
update macros

$\mathsf{beta}(\alpha, \beta)$ is the beta function with two arguments $\alpha$ and $\beta$.

@@

% \twocolumn{
\begin{equation*}
\boxed{
\begin{split}
\hlg(
beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
& <  \hlg(
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
\sqrt{1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
}
}
}
& < \sqrt{1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
\frac{\frac{n}{2} + 1 - 1 + \frac{n}{2} + 1 - 2}{2}, )}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
\mathsf{beta}(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
}
}
}\\
\sqrt{1 - \frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
}
}
}
& < \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
\mathsf{beta}(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}
}\\
\frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} + 1)
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
}
}
& > \frac{\mathsf{beta}(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2, \frac{n}{2})
\mathsf{beta}(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}\\
\frac{\mathsf{beta}(\frac{n + 3}{2},\frac{n - 1}{2}) 
\frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
\frac{\frac{n}{2}}{\frac{n}{2} + \frac{n}{2} + 1}}}
& > \frac{
\mathsf{beta}(\frac{n + 3}{2}, \frac{n - 1}{2}) 
\frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
\frac{\frac{n}{2} + 2}{\frac{n}{2} + 2 + \frac{n}{2} - 1}}}\\
\frac{\frac{n - 1}{2}}{\sqrt{(\frac{n}{2} - 1)(\frac{n}{2})}}
& > \frac{\frac{n + 3}{2}}{\sqrt{(\frac{n}{2} + 1)(\frac{n}{2} + 2)}}\\
(n - 1) ^ 2 (n + 2)(n + 4)
& > (n + 3) ^ 2 n (n - 2)\\
n & > -1.
\end{split}
}
\end{equation*}

@@

\begin{small}
\begin{equation*}
\begin{split}
& \sqrt{
1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + m + \frac{n}{2} + 1 + m + 1}{2},
\frac{\frac{n}{2} + 1 - m + \frac{n}{2} + 1 - m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}
}\\
& < \sqrt{
1 - \frac{\mathsf{beta}(
\frac{\frac{n}{2} + 1 + m + 1 + \frac{n}{2} + 1 + m + 2}{2},
\frac{\frac{n}{2} + 1 - m - 1 + \frac{n}{2} + 1 - m - 2}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
}\\
\\
& \frac{\mathsf{beta}(\frac{n + 2m + 3}{2}, \frac{n - 2m + 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}\\
& > \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
\end{split}
\end{equation*}
\end{small}

@@

From $x = x_0 + m$ and property of $\mathsf{beta}(\alpha, \beta)$ function, we know:
\vspace*{9.5cm}

\begin{footnotesize}
\begin{equation*}
\begin{split}
& \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
\frac{n - 2m - 1}{n + 2m + 3}}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m}{n + 2m + 2}
}
}\\
> & \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
\frac{n - 2m - 3}{n + 2m + 5}}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m - 2}{n + 2m + 6}
}
}\\
\end{split}
\end{equation*}

\begin{equation*}
\begin{split}
& \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
> & \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
\\
& \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
< & \sqrt{1 - \frac{\mathsf{beta}(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\mathsf{beta}(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\mathsf{beta}(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
\\
& \hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))\\
< & \hlg(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
\end{split}
\end{equation*}
\end{footnotesize}

>>>>

$\betafun(\alpha, \beta)$ is the beta function with two arguments $\alpha$ and $\beta$.

@@

% \twocolumn{
\begin{equation*}
\boxed{
\begin{split}
\hlg(
beta(\frac{n}{2} + 1, \frac{n}{2} + 1), 
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1))
& <  \hlg(
beta(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1), 
beta(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2))\\
\sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 + 1}{2},
\frac{\frac{n}{2} + 1 + \frac{n}{2} + 1 - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
}
}
}
& < \sqrt{1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + 1 + \frac{n}{2} + 1 + 2}{2}, 
\frac{\frac{n}{2} + 1 - 1 + \frac{n}{2} + 1 - 2}{2}, )}
{\sqrt{
\betafun(\frac{n}{2} + 1 + 1, \frac{n}{2} + 1 - 1)
\betafun(\frac{n}{2} + 1 + 2, \frac{n}{2} + 1 - 2)
}
}
}\\
\sqrt{1 - \frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
}
& < \sqrt{1 - \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} + 1)
\betafun(\frac{n}{2} + 2, \frac{n}{2})
}
}
& > \frac{\betafun(\frac{n + 5}{2}, \frac{n - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2, \frac{n}{2})
\betafun(\frac{n}{2} + 3, \frac{n}{2} - 1)
}
}\\
\frac{\betafun(\frac{n + 3}{2},\frac{n - 1}{2}) 
\frac{\frac{n - 1}{2}}{\frac{n - 1}{2} + \frac{n + 3}{2}}}
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} - 1}{\frac{n}{2} - 1 + \frac{n}{2} + 1} 
\frac{\frac{n}{2}}{\frac{n}{2} + \frac{n}{2} + 1}}}
& > \frac{
\betafun(\frac{n + 3}{2}, \frac{n - 1}{2}) 
\frac{\frac{n + 3}{2}}{\frac{n + 3}{2} + \frac{n - 1}{2}} }
{\sqrt{
\betafun(\frac{n}{2} + 1, \frac{n}{2} - 1) 
\frac{\frac{n}{2} + 1}{\frac{n}{2} + 1 + \frac{n}{2} - 1}
\frac{\frac{n}{2} + 2}{\frac{n}{2} + 2 + \frac{n}{2} - 1}}}\\
\frac{\frac{n - 1}{2}}{\sqrt{(\frac{n}{2} - 1)(\frac{n}{2})}}
& > \frac{\frac{n + 3}{2}}{\sqrt{(\frac{n}{2} + 1)(\frac{n}{2} + 2)}}\\
(n - 1) ^ 2 (n + 2)(n + 4)
& > (n + 3) ^ 2 n (n - 2)\\
n & > -1.
\end{split}
}
\end{equation*}

@@

\begin{small}
\begin{equation*}
\begin{split}
& \sqrt{
1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + m + \frac{n}{2} + 1 + m + 1}{2},
\frac{\frac{n}{2} + 1 - m + \frac{n}{2} + 1 - m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}
}\\
& < \sqrt{
1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + m + 1 + \frac{n}{2} + 1 + m + 2}{2},
\frac{\frac{n}{2} + 1 - m - 1 + \frac{n}{2} + 1 - m - 2}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
}\\
\\
& \frac{\betafun(\frac{n + 2m + 3}{2}, \frac{n - 2m + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}\\
& > \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
\end{split}
\end{equation*}
\end{small}

@@

From $x = x_0 + m$ and property of $\betafun(\alpha, \beta)$ function, we know:
\vspace*{9.5cm}

\begin{footnotesize}
\begin{equation*}
\begin{split}
& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
\frac{n - 2m - 1}{n + 2m + 3}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m}{n + 2m + 2}
}
}\\
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
\frac{n - 2m - 3}{n + 2m + 5}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m - 2}{n + 2m + 6}
}
}\\
\end{split}
\end{equation*}

\begin{equation*}
\begin{split}
& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
\\
& \sqrt{1 - \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
< & \sqrt{1 - \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
\\
& \hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))\\
< & \hlg(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
\end{split}
\end{equation*}
\end{footnotesize}
